Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-28 paper/ms.tex
there is evidence for two families, not three

The second constraint  comes from the angular correlation function (ACF)
for all the models having the $15$ mock surveys consistent with
observations . The ACF is computed  ( using 
the Davis \& Peebles  estimator \citep{Davis1983} ) only on the densest
sub-field in all the 15 mock surveys corresponding to the SSA22
region. We then take the mean ACF over the 15  mock surveys  for
each model as well as its the standard deviation to include
the effect of cosmic variance.

We finally compare the observational ACF and the mean mock  ACF of the models   
in therms of the angular correlation length ($\theta_{0}$) by fitting 
them to a power-law function:

@@

Both mock and observational ACF are derived by a least
square minimization procedure. The observational errors of 
the ACF as well as the standard deviation of the mean modeled ACFs  are
considered to compute the error in the fitted parameters to ensure ourselves
to include poissonian and cosmic-variance errors. 
We consider that a model is consistent with observations if the two
parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$ range.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}  
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Hayashino2004} and
\citet{Ouchi2010}. The error bars in the   theoretical data correspond
to the standard deviation from the different mocks surveys. 
%Right:
%Same results in the $\theta_{0}$-$M_{\rm min}$ plane, with the
%observational constraint on $\theta_{0}$ epresented by the red
%rectangle. Blue  squares represent models with $\log_{10} M_{\rm
%  max}<12.0$, green circles correspond to models with $\log_{10}
%M_{\rm max}>12.0$. 
\label{fig:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$
  vs $f_{\rm occ}$ (right). The squares represent the models when both
   constraints on the maximal number of  consistent mocks and the
  angular correlation function are included. 
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1& 10.2& 0.1\\
10.3& 10.5& 0.1\\
10.4& 10.7& 0.1\\
10.5& 10.6& 0.3\\
10.5& 10.9& 0.1\\
10.5& 11.0& 0.1\\
10.6& 10.8& 0.2\\
10.6& 11.2& 0.1\\
10.6& 11.3& 0.1\\
10.6& 11.4& 0.1\\
10.6& 11.5& 0.1\\
10.6& 11.6& 0.1\\
10.7& 11.0& 0.2\\
10.8& 11.2& 0.2\\
10.8& 11.3& 0.2\\
10.8& 11.4& 0.2\\
10.9& 11.3& 0.3\\
10.9& 11.7& 0.2\\
10.9& 11.8& 0.2\\
10.9& 11.9& 0.2\\
11.0& 11.6& 0.3\\
11.0& 11.7& 0.3\\
11.0& 11.8& 0.3\\
11.0& 12.0& 0.3\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow   mass range $\Delta M\leq 1.0$dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.6& 10.7& 0.4\\
10.7& 10.8& 0.5\\
10.8& 10.9& 0.6\\
10.8& 11.0& 0.4\\
10.9& 11.0& 0.8\\
10.9& 11.0& 0.9\\
10.9& 11.1& 0.5\\
11.0& 11.1& 1.0\\
11.0& 11.4& 0.4\\
11.1& 11.3& 0.7\\
11.1& 11.7& 0.4\\
11.2& 11.5& 0.7\\
11.2& 11.6& 0.6\\
11.2& 11.9& 0.5\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second family of models. Narrow
  mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.6& 11.7& 0.1\\
10.9& 12.1& 0.2\\
10.9& 12.2& 0.2\\
10.9& 12.3& 0.2\\
10.9& 12.4& 0.2\\
10.9& 12.5& 0.2\\
10.9& 12.6& 0.2\\
10.9& 12.7& 0.2\\
10.9& 12.8& 0.2\\
10.9& 12.9& 0.2\\
10.9& 13.&0 0.2\\\hline\hline
\end{tabular}
\end{center}
\caption{\label{table:thirdfamily}List of parameters for the third family of models. Broad
  mass range $\Delta M >1.0$dex and low occupation fraction $f_{\rm occ}\leq0.3$.}
\end{table}

>>>>

The second constraint  comes from the angular correlation function (ACF)
for all the models having the $15$ mock surveys consistent with
observations . The ACF is computed  ( using 
the Landy \&  Szalay  estimator \citep{Landy1993} )  on two kinds of
fields in the mock survey: the densest and one corresponding to the
average density. The first with the \cite{Hayashino2004}  and \cite{Ouchi2010}
ACFs respectively.

The observational ACF and the  mock  ACF of the models are compared   
in terms of the correlation length ($\theta_{0}$) by fitting 
them to a power-law function:

@@

Both mock and observational ACF are derived by a least square
minimization procedure. For each mock we obtain a covariance matrix
that gives us the uncertainty in the parameters $\beta$ and
$\theta_0$. We compute a mean value for the parameters and its
associated uncertainty as the cuadratic average of the uncertainties in
the fitting procedure. We consider that a model is consistent with
observations if the two parameters $\beta$ and $\theta_0$ are equal
within a $1$-$\sigma$ range.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_maxden.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_meanden.pdf} 
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}  
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Hayashino2004} and
\citet{Ouchi2010}. The error bars in the   theoretical data correspond
to the standard deviation from the different mocks surveys. 
%Right:
%Same results in the $\theta_{0}$-$M_{\rm min}$ plane, with the
%observational constraint on $\theta_{0}$ epresented by the red
%rectangle. Blue  squares represent models with $\log_{10} M_{\rm
%  max}<12.0$, green circles correspond to models with $\log_{10}
%M_{\rm max}>12.0$. 
\label{fig:correlation_parameters}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_f_occ.pdf}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$
  vs $f_{\rm occ}$ (right). The squares represent the models when both
   constraints on the maximal number of consistent mocks and the
  angular correlation function are included. Upper panels correspond
  checks the consistency against the observational data of
  \citet{Ouchi2010}, while lower panels show results for \citet{Hayashino2004}
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1 &10.2 & 0.1\\
10.3 &10.5 & 0.1\\
10.4 &10.7 & 0.1\\
10.5 &10.6 & 0.3\\
10.5 &10.9 & 0.1\\
10.5 &11.0 & 0.1\\
10.6 &11.2 & 0.1\\
10.6 &11.4 & 0.1\\
10.6 &11.7 & 0.1\\
10.7 &11.0 & 0.2\\
10.8 &11.2 & 0.2\\
10.8 &11.3 & 0.2\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.6 &10.7 &0.4\\
10.8 &10.9 &0.6\\
10.8 &11.0 &0.4\\
10.9 &11.0 &0.8\\
10.9 &11.0 &0.9\\
10.9 &11.1 &0.5\\
11.0 &11.1 &1.0\\
11.1 &11.3 &0.8\\
11.2 &11.6 &0.6\\
11.2 &12.2 &0.5\\
11.3 &11.7 &0.9\\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}
